Papers

### 2024-07-17 papers.qmd
update

@@

>>>>

-   Stafford T, Rombach I, Hind D et al. Where next for partial randomisation of research funding? The feasibility of RCTs and alternatives [version 2; peer review: 3 approved]. Wellcome Open Res 2024, 8:309 (<https://doi.org/10.12688/wellcomeopenres.19565.2>)

@@

- Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., … Forstmann, B. (2024, July 2). [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp). https://doi.org/10.31234/osf.io/snqgp
